---
title: "Data Analysis"
author: "Tim Abramov"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(dplyr)

games_features <- read_xlsx("games_features.xlsx")
##we need only games:
games <- filter(game_features, GenreIsNonGame == FALSE)
```

## Question 1
"Are there any qualitative differences that can be measured between games that received a Metacritic score and those that didn't?"
```{r echo = FALSE}
##then group by if metacritic != 0 (one group of games that received the score, and one that didn't)

```


## Question 2
"Does length of game description or number of game screenshots have a measurable effect on the sales of the game?"
```{r echo = FALSE}
##regression analysis 


##ScreenshotCount vs. SteamSpyOwners

##1. Scatterplot
scatter.smooth(x=games$ScreenshotCount, y=games$SteamSpyOwners, main="ScreenshotCount ~ SteamSpyOwners")
##2. BoxPlots
par(mfrow=c(1, 2))  # divide graph area in 2 columns
boxplot(games$ScreenshotCount, main="ScreenshotCount",
sub=paste("Outliers: ", length(boxplot.stats(games$ScreenshotCount)$out)))  # box plot for ScreenshotCount
boxplot(games$SteamSpyOwners, main="SteamSpyOwners",
sub=paste("Outliers: ", length(boxplot.stats(games$SteamSpyOwners)$out)))  # box plot for SteamSpyOwners
##3. Density plot (check for normality of the data)
##4. Linear model?

##length(DetailedDescrip) vs. SteamSpyOwners

```


## Question 3
"Is there an association between how many copies of the game were sold and the price of the game?"
```{r echo = FALSE}
##regression analysis
##SteamSpyOwners vs. PriceFinal

```

