---
title: "Data Analysis"
author: "Tim Abramov"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(dplyr)

games_features <- read_xlsx("games_features.xlsx")
##we need only games:
games <- filter(game_features, GenreIsNonGame == FALSE)
```

## Question 1
"Are there any qualitative differences that can be measured between games that received a Metacritic score and those that didn't?"
```{r echo = FALSE}
##then group by if metacritic != 0 (one group of games that received the score, and one that didn't)

```


## Question 2
"Does length of game description or number of game screenshots have a measurable effect on the sales of the game?"
```{r echo = FALSE}
##do a regression analysis num of words vs. sales(owners)
##and num of screenshots vs. sales(owners)
```


## Question 3
"Is there an association between how many copies of the game were sold and the price of the game?"
```{r echo = FALSE}
##most likely a regression analysis here too
##num of owners vs. price(final)
```

